An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-23 paper.tex
Provide proper proof of Theorem 1

\begin{thm}[Correctness of the evolving graph BFS]
Algorithm~\ref{alg:bfs} discovers every active node that is reachable from the
root $(v_1, t_1)$, and $reached[(v, t)]$ is the distance from $(v_1, t_1)$ to
$(v, t)$.
\end{thm}

\proof
Define a static graph $G=(V,E)$ with node set $V = $V^{[1]}$ $\{t\}, t\in\{t_1, t_2, \dots, t_n\}$  such that We could map an evolving graph $G_n$ to a static graph $G$ in such a way that
if there is an edge from $(v, t)$ to $(u,t)$ in $G_n$, there is an edge from $v_t$ to $u_t$ in $G$.
For any two nodes $v_s$ and $v_t$ in $G$, if $s < t$, we add an edge from $v_s$ to $v_t$.
By construction, an active node $(v,t)$ in $G_n$ is in one-to-one correspondence with
a node $v_t$ in $G$.
The forward-neighbors of an active node $(v, t)$ in $G_n$
are in one-to-one correspondence with the forward-neighbors of a node $v_t$ in $G$.
Hence the correctness of the evolving graph BFS follows from that of a static graph.
\endproof

@@

\begin{thm}
 Algorithm \ref{alg:bfs} and Algorithm \ref{alg:bfsla} are equivalent.
\end{thm}
\proof
We shall check the two algorithms are equivalent in each module of
the method.
The initialization steps are trivially equivalent.
By the construction of $\bm{A^T}$,
step $9$ of Algorithm \ref{alg:bfsla} computes the forward-neighbors
of all the frontier nodes, which is equivalent to step $8$-$9$
of Algorithm \ref{alg:bfs}. Step $10$-$15$ of Algorithm \ref{alg:bfsla} ensures
active nodes will not be visited twice, which is equivalent to step $10$
of Algorithm \ref{alg:bfs}. Finally, a dictionary $dict$ is used by both algorithms
to keep record of the distance of each node from the source $(s,t)$.
\endproof

>>>>

\begin{thm}[Correctness of the evolving graph BFS]
Let $G_n$ be an evolving graph and $(v_1, t_1)$ be an active node of $G_n$.
Then Algorithm~\ref{alg:bfs} discovers every active node that is reachable from
the root $(v_1, t_1)$, and $reached[(v, t)]$ is the distance from $(v_1, t_1)$
to $(v, t)$.
\end{thm}

\IEEEproof
Define the set of temporal nodes
$\tilde V_L^{[t]} = \{(v_1)_t = (v_1, t) | (v_1, v_2) \in E^{[t]}\}$, which
consists of the active nodes at time $t$ which participate on the left side of an edge.
Similarly, $\tilde V_R^{[t]} = \{(v_2)_t = (v_2, t) | (v_1, v_2) \in E^{[t]}\}$
are the corresponding active nodes on the right side of an edge. Then
$\tilde V^{[t]} = \tilde V_L^{[t]} \cup \tilde V_R^{[t]}$ is the set of active
nodes at time $t$, and $V = \bigcup_t \tilde V^{[t]}$ is the set of all
active nodes in $G_n$.

Similarly, define an edge set $E' = \{(u_s,v_t)|u_s=(u,s)\in V,
v_t=(v,t)\in V, v=u, s<t\}$, which consists of temporal nodes that connect
active nodes sharing the same node at different times. Each edge in $E'$ is then
in 1-1 correspondence with a temporal path of length 2,
$\langle (v,s), (v,t) \rangle$.
Define also $\tilde E^{[t]} = \{(e, t)|e\in E^{[t]}\}$, which are simply the edge
sets in $G_n$ with time labels. Then $E = \bigcup_t \tilde E^{[t]} \cup E'$ is
the set of all edges representing all allowed temporal paths of length 2.

The node set $V$ and edge set $E$ now define a static graph $G=(V,E)$ that is in
1-1 correspondence with the evolving graph $G_n$. The node set $V$ of $G$ is in
1-1 correspondence with active nodes of $G_n$ while the edge set $E$ is in 1-1
correspondence with all temporal paths of length 2 on $G_n$.

We now establish a similar 1-1 correspondence of forward neighbors of an active
node with a subset of $G$.
By definition, the forward neighbors of some active node $(v, t) \in G_n$ are
active nodes of either the form $(v, t')$ for some $t' > t$ or $(u, t)$ for some
$u\ne v$. Clearly, the former are elements of $E' \subseteq E$ while the latter
are elements of $E^{[t]} \subseteq \bigcup_s \tilde E^{[s]} \subseteq E$.
Thus each forward neighbor of an active node $(v, t) \in G_n$ is in 1-1
correspondence with a node in $V$ that is a neighbor of $v_t \in V$.

The correctness of BFS on the evolving graph $G_n$ now follows from the
correctness of BFS on the static graph $G$, since we have also established a 1-1
correspondence for every intermediate quantity in Algorithm~\ref{alg:bfs}.
\endproof

@@

\begin{thm}
 Algorithm \ref{alg:bfs} and Algorithm \ref{alg:bfsla} are equivalent.
\end{thm}

\IEEEproof
We shall check the two algorithms are equivalent in each module of
the method.
The initialization steps are trivially equivalent.
By the construction of $\bm{A^T}$,
step $9$ of Algorithm \ref{alg:bfsla} computes the forward-neighbors
of all the frontier nodes, which is equivalent to step $8$-$9$
of Algorithm \ref{alg:bfs}. Step $10$-$15$ of Algorithm \ref{alg:bfsla} ensures
active nodes will not be visited twice, which is equivalent to step $10$
of Algorithm \ref{alg:bfs}. Finally, a dictionary $dict$ is used by both algorithms
to keep record of the distance of each node from the source $(s,t)$.
\endproof
